{\bf Systematic Testing: A New Perspective on Races}

### 2014-04-02 landslide-lecture/lecture.tex
fix about-the-project slide and add citation
cleanup other things i guess
update landslide lecture for s2014

\title[Landslide]{{\bf Systematic Dynamic Race Condition Detection}}
\subtitle[]{ {\em more clever than } ``\texttt{slaughter cho2}'' {\em since 2011.}}
\author[Ben Blum]{Ben Blum \texttt{(bblum@andrew.cmu.edu)}}

\institute[CMU 15-410]{Carnegie Mellon University - 15-410}
\date[]{2013, April 14}

@@

@@

\begin{frame}{Outline}
	\textbf{Theory: Seeing race conditions in a new way}
	\begin{itemize}
		\item Case study (example)
		\item The execution tree
		\item Decision points
	\end{itemize}
	{\bf Technique: Systematic testing}
	% Say: A way of enumerating all possible interleavings of a concurrent test case.
	\begin{itemize}
		\item Requirements
		\item Challenges and feasibility
	\end{itemize}
	{\bf Tool: Landslide}
	\begin{itemize}
		\item How it works
		\item The user-tool relationship
		\item User study (that's you!)
			% !!! SAY !!! : If you are struggling, this is not for you, etc.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Decision Points (``good'' case)}
	\begin{tabular}{|l|l|l}
		\cline{1-2}
		{\bf Thread 1} & {\bf Thread 2} & \\
		\cline{1-2}
		\texttt{spawn\_new\_thread} && \\
		\cline{1-2}
		\texttt{add\_to\_runqueue} && (new thread) \\
		\cline{1-2}
		\texttt{return child->tid} &&  \\
		\cline{1-2}
		& \texttt{vanish} & \\
		\cline{1-2}
		& (TCB gets freed) & (voluntary reschedule) \\
		\cline{1-2}
	\end{tabular}
\end{frame}

\begin{frame}{Decision Points (race condition)}
	\begin{tabular}{|l|l|l}
		\cline{1-2}
		{\bf Thread 1} & {\bf Thread 2} & \\
		\cline{1-2}
		\texttt{spawn\_new\_thread} && \\
		\cline{1-2}
		\texttt{add\_to\_runqueue} && (new thread + preempted) \\
		\cline{1-2}
		& \texttt{vanish} & \\
		\cline{1-2}
		& (TCB gets freed) & (voluntary reschedule) \\
		\cline{1-2}
		\texttt{return child->tid} && (bad!) \\
		\cline{1-2}
	\end{tabular}
\end{frame}

@@

\begin{frame}{Decision Points} % TODO: duplicate slide with later
	A {\bf decision point} is\ldots

@@

\begin{frame}{Systematic Testing}
	\textbf{Systematic testing} is:
	\begin{itemize}
		\item Systematically enumerating different interleavings
		\begin{itemize}
			\item Intuitively: Generate many ``tabular execution traces''
		\end{itemize}
		\item Exploring all branches in these trees
		\begin{itemize}
			\item (by controlling scheduling decisions at decision points)
		\end{itemize}
		\item In practice: Depth-first search of branches
	\end{itemize}
\end{frame}

@@

\begin{frame}{Execution Tree Exploration}
	Important point: When does a branch end?
	\begin{itemize}
		\item All threads run to completion, or
		\item A bug is detected % Say: more on this later.
	\end{itemize}
	\linegap
	{\bf Backtracking}:
	\begin{itemize}
		\item Identify a decision point to choose differently
		\item Reset machine state and start over
		\item Replay test from the beginning, with different ``decisions''
	\end{itemize}
\end{frame}

\begin{frame}{More on Decision Points}
	Important point: What does ``all possible interleavings'' mean?

@@

	Other extreme: Nothing is a decision point
	\begin{itemize}
		\item {\em Good news}: Test will finish quickly.
		\item {\em Bad news}: Only one execution was checked for bugginess.
		\item {\em Bad news}: No alternative interleavings explored.
		\begin{itemize}
			\item Makes ``no race found'' a weak claim.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{More on Decision Points}
	Sweet spot: Insert a thread switch everywhere it ``might matter''.

@@

\begin{frame}{Controlling Scheduling Decisions}
	Control over sources of nondeterminism
	\begin{itemize}
		\item Device interrupts/input
			\begin{itemize}
				\item Disk drivers: when disk reads finish
				\item Ethernet drivers: when packets arrive
			\end{itemize}
		\item To control thread switches in a 410 kernel, vary when clock ticks happen.
	\end{itemize}
\end{frame}

\begin{frame}{Memory Interposition}
	In order to find use-after-free, need to know:
	\begin{itemize}
		\item When objects are \texttt{free()}d
		\item When threads access shared memory in the heap
	\end{itemize}
	\linegap

@@

\begin{frame}{State Space Explosion}
	State spaces grow exponentially
	\begin{itemize}
		\item With $d$ decision points, $k$ runnable threads, size $d^k$.
		\item Threatens our ability to explore everything.
		\item Fortunately, some sequences result in identical states.
	\end{itemize}
	\linegap

	{\bf Partial Order Reduction} can help.
	\begin{itemize}
		\item Complicated algorithm; ask me later for details.
		\item Intuitive explanation follows.
	\end{itemize}
\end{frame}

@@

\begin{frame}{About The Project}
	5th year MS since June 2011 % Say: planning to finish this may, hopefully
	My MS thesis project (June 2011-2012)

@@

\begin{frame}{Landslide in Simics}
	As a Simics module, Landslide knows:
	\begin{itemize}
		\item Every instruction the kernel executes
		\item Every memory address the kernel reads/writes
	\end{itemize}
	\linegap
	Artificially causes timer interrupts

@@

\begin{frame}{In Which Ben Offers Help}
	% Say: So, this wasn't just a research talk
	This is something you can try!
	\linegap

@@

\begin{frame}{Keeping It Real}
	Finding race conditions is hard for humans.

@@

\begin{frame}{Annotating Your Kernel}
	Step 1
	\begin{center}
		\includegraphics[width=0.9\textwidth]{tell_landslide.png}
	\end{center}
	Your kernel needs to say when certain events happen:
	\begin{itemize}
		\item When do threads become runnable / descheduled?
		\item When does the scheduler switch threads?
	\end{itemize}
\end{frame}

\begin{frame}{Configuring Landslide}
	Step 2
	\begin{center}
		\includegraphics[width=0.8\textwidth]{config-landslide.png}
	\end{center}
	Edit \texttt{config.landslide} with some details and tweaks

	Fill in two implementation-dependent C functions in Landslide ($\le$10 lines)
	% Say: Which depend on your kernel's specific implementation
\end{frame}

\begin{frame}{Configuring Decision Points}
	Landslide automatically identifies a minimal set of decision points.
	\begin{itemize}
		\item It might find bugs.
		\item It might overlook more fine-grained interleavings.
	\end{itemize}
	\linegap
	With help from you, it could find more.
	\begin{itemize}
		\item Optional annotation: \texttt{tell\_landslide\_decide()}
		\item Hints to where a context switch should be forced.
		\item Inside every call to \texttt{mutex\_lock}\ldots
	\end{itemize}
\end{frame}

\begin{frame}{And Hopefully\dots}
	\begin{center}
		\includegraphics[width=\textwidth]{found_a_bug.png}
	\end{center}
\end{frame}

@@

%\begin{frame}{Decision Points (noticing a theme here?)}
%	Landslide is {\bf false negative}-oriented.
%	\begin{itemize}
%		\item If Landslide reports a bug, there is a bug for sure.
%			% Say: Well, except progress sense might be wrong.
%		\item If not,
%			\begin{itemize}
%				\item Maybe there was no race, or
%				\item Maybe your decision points were not granular enough.
%			\end{itemize}
%	\end{itemize}
%\end{frame}
%\begin{frame}{Decision Points (noticing a theme here?)}
%	Sometimes the default set will work.
%
%	Sometimes you need to tweak\ldots
%	\begin{itemize}
%		\item Ignore certain global mutexes
%		\item Whitelist or blacklist entire syscalls
%		\item (get creative)
%	\end{itemize}
%	Intuitively: focusing Landslide on relevant parts of the kernel.
%\end{frame}

@@

\begin{frame}{Last Year's Results}
	\begin{itemize}
		\item Worked with 5 groups
		\begin{itemize}
			\item \dots{}of which 4 put in enough time to make Landslide work
		\end{itemize}
		\linegap
		\item {\bf Investment}: about 2 to 3 hours
		\begin{itemize}
			\item Average 112 minutes doing required instrumentation
			\item Average 35 minutes configuring extra decision points \& interpreting ``found a bug'' output
		\end{itemize}
		\pause
		\linegap
		\item {\bf Return}: All 4 groups found bugs in their kernels.
		\begin{itemize}
			\item All groups found deterministic bugs (e.g., use-after-free)
			\item 2 groups found race conditions (i.e., Landslide needed to backtrack)
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{In Which Ben Offers Help - Warning}
	\textbf{If you are already struggling, this will not ``save'' you.}
	\begin{itemize}
		\item False-negatives: not guaranteed to find races at all
		\item Research-quality: possibly difficult to integrate with your kernel
		\item Finishing the kernel project is more important.
	\end{itemize}
	\pause
	\linegap
	This is for you if:
	\begin{itemize}
		%\item Be expecting an A or a B
		\item You have already submitted
		\item You are using late days, but willing to work over Carnival
		%\item Be able to turn in without late days (if you really had to)
		\item You are taking p3extra, but you already pass the hurdle
		\item You are looking for\ldots
			\begin{itemize}
				\item That ``one pesky race''
				\item A race that stress-testing missed
				\item Or just familiarity with a new technique
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{In Which Ben Offers Help}
	Your kernel
	\begin{itemize}
		\item Must load the shell and run programs
		\item \texttt{fork},
			\texttt{exec},
			\texttt{vanish},
			\texttt{wait},
			\texttt{readline}
		\item Must never spin-wait (see hurdle form!)
		\item Should \texttt{assert()} important invariants
		\begin{itemize}
			\item Think of \texttt{panic()} as \texttt{tell\_landslide\_bug()}
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{In Which Ben Offers Help}
	User study this week, by appointment (\texttt{bblum@cs.cmu.edu})

>>>>

\title[Landslide]{{\bf Systematic Testing: A New Perspective on Races}}
\subtitle[]{ {\em more clever than } ``\texttt{slaughter cho2}'' {\em since 2011.}}
\author[Ben Blum]{Ben Blum \texttt{(bblum@andrew.cmu.edu)}}

\institute[CMU 15-410]{Carnegie Mellon University - 15-410}
\date[]{2014, April 2}

@@

\newcommand\hilight[2]{\color{#1}#2\color{black}}
\definecolor{olivegreen}{RGB}{0,127,0}

@@

\begin{frame}{Outline}
	\textbf{Theory: Seeing race conditions in a new way}
	\begin{itemize}
		\item Case study (example)
		\item The execution tree
		\item Preemption points
	\end{itemize}
	{\bf Technique: Systematic testing}
	% Say: A way of enumerating all possible interleavings of a concurrent test case.
	\begin{itemize}
		\item Requirements
		\item Challenges and feasibility
	\end{itemize}
	{\bf Tool: Landslide}
	\begin{itemize}
		\item How it works
		\item The user-tool relationship
		\item User study (that's you!)
			% !!! SAY !!! : If you are struggling, this is not for you, etc.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Thread Interleavings (``good'' case)}
	\begin{tabular}{|l|l|l}
		\cline{1-2}
		{\bf Thread 1} & {\bf Thread 2} & \\
		\cline{1-2}
		\texttt{spawn\_new\_thread} && \\
		\cline{1-2}
		\texttt{add\_to\_runqueue} && (new thread) \\
		\cline{1-2}
		\texttt{return child->tid} &&  \\
		\cline{1-2}
		& \texttt{vanish} & \\
		\cline{1-2}
		& (TCB gets freed) & (voluntary reschedule) \\
		\cline{1-2}
	\end{tabular}
\end{frame}

\begin{frame}{Thread Interleavings (race condition)}
	\begin{tabular}{|l|l|l}
		\cline{1-2}
		{\bf Thread 1} & {\bf Thread 2} & \\
		\cline{1-2}
		\texttt{spawn\_new\_thread} && \\
		\cline{1-2}
		\texttt{add\_to\_runqueue} && (new thread + preempted) \\
		\cline{1-2}
		& \texttt{vanish} & \\
		\cline{1-2}
		& (TCB gets freed) & (voluntary reschedule) \\
		\cline{1-2}
		\texttt{return child->tid} && (bad!) \\
		\cline{1-2}
	\end{tabular}
\end{frame}

\begin{frame}{Testing}
	How can programmers be confident in their code's correctness?
	\begin{itemize}
		\item Theorem proving
		\item Unit tests
		\item Stress tests
		\begin{itemize}
			\item (state of the art in 15-410)
		\end{itemize}
		\item Releasing to paying customers and worrying about correctness later
	\end{itemize}
	\linegap

	{\bf Motivation}: Can we do better than stress testing?
\end{frame}

@@

\begin{frame}{Preemption Points} % TODO: duplicate slide with later
	A {\bf preemption point} is\ldots

@@

\begin{frame}{Systematic Testing}
	\textbf{Systematic testing} is:
	\begin{itemize}
		\item Systematically enumerating different interleavings
		\begin{itemize}
			\item Intuitively: Generate many ``tabular execution traces''
		\end{itemize}
		\item Exploring all branches in these trees
		\begin{itemize}
			\item (by controlling scheduling decisions at preemption points)
		\end{itemize}
		\item In practice: Depth-first search of branches
	\end{itemize}
\end{frame}

@@

\begin{frame}{Execution Tree Exploration}
	Important point: When does a branch end?
	\begin{itemize}
		\item All threads run to completion, or
		\item A bug is detected % Say: more on this later.
	\end{itemize}
	\linegap
	{\bf Backtracking}:
	\begin{itemize}
		\item Identify a preemption point to replay differently
		\item Reset machine state and start over
		\item Replay test from the beginning, with different preemptions
	\end{itemize}
\end{frame}

\begin{frame}{More on Preemption Points}
	Important point: What does ``all possible interleavings'' mean?

@@

	Other extreme: Nothing is a preemption point
	\begin{itemize}
		\item {\em Good news}: Test will finish quickly.
		\item {\em Bad news}: Only one execution was checked for bugginess.
		\begin{itemize}
			\item No alternative interleavings explored.
			\item Makes ``no race found'' a weak claim.
		\end{itemize}
	\end{itemize}
	\linegap

	Is there a ``sweet spot''?
\end{frame}

\begin{frame}{More on Preemption Points}
	Sweet spot: Insert a thread switch everywhere it ``might matter''.

@@

\begin{frame}{Controlling Scheduling Decisions}
	How do we control which thread runs when?
	\linegap

	In other words, what sources of nondeterminism must we control?

	\begin{itemize}
		\item Device interrupts/input
			\begin{itemize}
				\item Disk drivers: when disk reads finish
				\item Ethernet drivers: when packets arrive
			\end{itemize}
		\item To control thread switches in a 410 kernel, vary when clock ticks happen.
	\end{itemize}
\end{frame}

\begin{frame}{Memory Interposition}
	How do we detect race-induced heap corruption?
	\linegap

	In order to find use-after-free, need to know:
	\begin{itemize}
		\item When objects are \texttt{free()}d
		\item When threads access shared memory in the heap
	\end{itemize}
	\linegap

@@

\begin{frame}{State Space Explosion}
	Serious problem: State spaces grow exponentially
	\begin{itemize}
		\item With $p$ preemption points and $k$ runnable threads, size $p^k$.
		\item Threatens our ability to explore everything.
		\item Fortunately, some sequences result in identical states.
	\end{itemize}
	\linegap

	{\bf Partial Order Reduction} can help.
	\begin{itemize}
		\item Intuitively: After exploring each interleaving, identify ``equivalent'' alternatives and skip over them.
		\item Example follows\dots
	\end{itemize}
\end{frame}

@@

\begin{frame}{About The Project}
	% 5th year MS since June 2011 % Say: planning to finish this may, hopefully
	My MS thesis project (2011-2012)
	\begin{itemize}
		\item {}[CMU-CS-12-118 -- \url{http://bblum.net/thesis.pdf}]
	\end{itemize}

@@

\begin{frame}{Landslide in Simics}
	As a Simics module, Landslide knows:
	\begin{itemize}
		\item Every instruction the kernel executes
		\item Every memory address the kernel reads/writes
	\end{itemize}
	\linegap
	Artificially causes timer interrupts to control scheduling

@@

\begin{frame}{Recruitment}
	% Say: So, this wasn't just a research talk
	This is something you can try!
	\linegap

@@

\begin{frame}{Words of Warning}
	Finding race conditions is hard for humans.

@@

\begin{frame}{Annotating Your Kernel}
	Step 1
	\begin{center}
		{\small
		\begin{tabular}{l}
		\texttt{\hilight{olivegreen}{int}~thread\_fork() \{} \\
	        \texttt{~~~~\hilight{olivegreen}{thread\_t}~*child = construct\_new\_thread();} \\
		\texttt{~~~~\hilight{purple}{tell\_landslide\_forking}();~\hilight{blue}{/* A new thread was created.~*/}} \\
	        \texttt{~~~~add\_to\_runqueue(child);} \\
	        \texttt{~~~~return child->tid;} \\
		\texttt{\}} \\
		\texttt{\hilight{olivegreen}{void}~add\_to\_runqueue(\hilight{olivegreen}{thread\_t}~*t) \{} \\
		\texttt{~~~~\hilight{blue}{/* This thread is now runnable.~*/}} \\
		\texttt{~~~~\hilight{purple}{tell\_landslide\_thread\_on\_rq}(t->tid);} \\
		\texttt{~~~~...} \\
		\texttt{\}} \\
		\end{tabular}
		}
	\end{center}
	Your kernel needs to say when certain events happen, for example:
	\begin{itemize}
		\item When do threads become runnable / descheduled?
		\item When does the scheduler switch threads?
	\end{itemize}
\end{frame}

\begin{frame}{Configuring Landslide}
	Step 2
	\begin{center}
		{\small
		\begin{tabular}{l}
		\texttt{\hilight{blue}{\# What test case to run?}} \\
		\texttt{\hilight{black}{TEST\_CASE}=\hilight{olivegreen}{"double\_thread\_fork"}} \\
		\texttt{} \\
		\texttt{\hilight{blue}{\# The names of some important functions~~~~~~~~~~~}} \\
		\texttt{\hilight{black}{TIMER\_WRAPPER}=\hilight{olivegreen}{"timer\_handler\_wrapper"}} \\
		\texttt{\hilight{black}{CONTEXT\_SWITCH}=\hilight{olivegreen}{"ctx\_switch"}} \\
		\texttt{} \\
		\texttt{\hilight{blue}{\# What functions to pay attention to?}} \\
		\texttt{within\_function \hilight{olivegreen}{"thread\_fork"}} \\
		\texttt{within\_function \hilight{olivegreen}{"vanish"}} \\
		\end{tabular}
		}
	\end{center}
	\linegap

	Fill out \texttt{config.landslide} with design details and names of important functions

	% Fill in two implementation-dependent C functions in Landslide ($\le$10 lines)
	% Say: Which depend on your kernel's specific implementation
\end{frame}

\begin{frame}{Configuring Preemption Points}
	Landslide automatically identifies a minimal set of preemption points.
	\begin{itemize}
		\item It might find bugs.
		\item It might overlook more fine-grained interleavings.
	\end{itemize}
	\linegap
	With help from you, it could find more.
	\begin{itemize}
		\item Optional annotation: \texttt{tell\_landslide\_preempt()}
		\item Hints to where a context switch should be forced.
		\item Inside every call to \texttt{mutex\_lock}\ldots
	\end{itemize}
\end{frame}

\begin{frame}{And Hopefully\dots}
	\begin{center}
	{\small
        \begin{tabular}{l}
        \texttt{\hilight{red}{USE AFTER FREE - read from 0x199630 at eip 0x104264}} \\
        \texttt{Heap contents:~\{...\}} \\
        \texttt{[0x199630 | 4140] was allocated by TID3 at (...)} \\
        \texttt{~~~~~~~~~~~~~~~~~~~~~~and freed by TID4 at (...)} \\
        \texttt{\hilight{red}{****~~~~~~A bug was found!~~~~~****}} \\
        \texttt{\hilight{red}{**** Preemption trace follows.~****}} \\
        \texttt{\hilight{olivegreen}{1:~~TID 3 -{}-> TID 4}} \\
        \texttt{~~~~TID3 at 0x105a10 in \hilight{blue}{context\_switch},} \\
        \texttt{~~~~~~~~~~~~0x1041f4 in \hilight{blue}{thread\_fork},} \\
        \texttt{~~~~~~~~~~~~0x10362b in \hilight{blue}{thread\_fork\_wrapper}} \\
        \texttt{\hilight{olivegreen}{2:~~TID 4 -{}-> TID 3}} \\
        \texttt{~~~~TID4 at 0x105a10 in \hilight{blue}{context\_switch},} \\
        \texttt{~~~~~~~~~~~~0x104681 in \hilight{blue}{yield},} \\
        \texttt{~~~~~~~~~~~~0x104570 in \hilight{blue}{vanish},} \\
        \texttt{~~~~~~~~~~~~0x103708 in \hilight{blue}{vanish\_wrapper}} \\
        \texttt{\hilight{red}{Current stack:}}\\
        \texttt{~~~~TID3 at 0x104209 in \hilight{blue}{thread\_fork},} \\
        \texttt{~~~~~~~~~~~~0x10362b in \hilight{blue}{thread\_fork\_wrapper}}
        \end{tabular}
	}

	\end{center}
\end{frame}

@@

%\begin{frame}{Preemption Points (noticing a theme here?)}
%	Landslide is {\bf false negative}-oriented.
%	\begin{itemize}
%		\item If Landslide reports a bug, there is a bug for sure.
%			% Say: Well, except progress sense might be wrong.
%		\item If not,
%			\begin{itemize}
%				\item Maybe there was no race, or
%				\item Maybe your preemption points were not granular enough.
%			\end{itemize}
%	\end{itemize}
%\end{frame}
%\begin{frame}{Preemption Points (noticing a theme here?)}
%	Sometimes the default set will work.
%
%	Sometimes you need to tweak\ldots
%	\begin{itemize}
%		\item Ignore certain global mutexes
%		\item Whitelist or blacklist entire syscalls
%		\item (get creative)
%	\end{itemize}
%	Intuitively: focusing Landslide on relevant parts of the kernel.
%\end{frame}

@@

\begin{frame}{Last Year's Results}
	\begin{itemize}
		\item Worked with 5 groups
		\begin{itemize}
			\item \dots{}of which 4 put in enough time to make Landslide work
		\end{itemize}
		\linegap
		\item {\bf Investment}: about 2 to 3 hours
		\begin{itemize}
			\item Average 112 minutes doing required instrumentation
			\item Average 35 minutes configuring extra preemption points \& interpreting ``found a bug'' output
		\end{itemize}
		\pause
		\linegap
		\item {\bf Return}: All 4 groups found bugs in their kernels.
		\begin{itemize}
			\item All groups found deterministic bugs (e.g., use-after-free)
			\item 2 groups found race conditions (i.e., Landslide needed to backtrack)
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Words of Warning Again}
	\textbf{If you are already struggling, this will not ``save'' you.}
	\begin{itemize}
		\item False-negatives: not guaranteed to find races at all
		\item Research-quality: possibly difficult to integrate with your kernel
		\item Finishing the kernel project is more important.
	\end{itemize}
	\pause
	\linegap
	This is for you if:
	\begin{itemize}
		%\item Be expecting an A or a B
		\item You have already submitted
		\item You are using late days, but willing to work over Carnival
		%\item Be able to turn in without late days (if you really had to)
		\item You are taking p3extra, but you already pass the hurdle
		\item You are looking for\ldots
			\begin{itemize}
				\item That ``one pesky race''
				\item A race that stress-testing missed
				\item Or just familiarity with a new technique
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Recruitment - Kernel Requirements}
	Your kernel
	\begin{itemize}
		\item Must load the shell and run programs
		\item \texttt{fork},
			\texttt{exec},
			\texttt{vanish},
			\texttt{wait},
			\texttt{readline}
		\item Must pass the hurdle architectural requirements
		\begin{itemize}
			\item especially: must never spin-wait!
		\end{itemize}
		\item Should \texttt{assert()} important invariants
		\begin{itemize}
			\item Think of \texttt{panic()} as \texttt{tell\_landslide\_bug()}
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Recruitment}
	User study this week, by appointment (\texttt{bblum@cs.cmu.edu})
